Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
mcudameme better explained

The other application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, is a classical molecular dynamics simulator that can be applied at the atomic, meso, or continuum scale. 
From the implementation perspective, this multi-process application employs at least one GPU to host its processes, but can benefit from the use of multiple GPUs.
The Figure shows that running this application using remote GPUs does not offer any advantage in front of original CUDA. 
Furthermore, for the execution on remote GPUs, can be seen a little difference between both networks, the ``High'' network performs worse than ``10 Gb'' network.
Thus, if we compare the results of a LAMMPS execution with a larger problem (see Figure), although CUDA continues performing better, the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks what means that the transfers are making the interconnection network the bottleneck, and enlarging the problem size
pays off the drawback of a slower network.

@@

\subsection{Experimental Results}
The test were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1090 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; the cloud platform is deployed by OpenStack; and
the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0.

@@

MCUDA-MEME~\cite{Liu2010} has been the application executed with
different configurations in order to test the set-ups. MCUDA-
MEME is GPGPU MPI application, so the number of GPUs
will determine the number of executable processes.
The Figure~\ref{fig3} shows and compares the execution time of
the application with different configurations over different set-
ups. We can determine that with 1 node, the performance is
lower, with 2 and 3 is quite similar, though. Hence, the greatest
difference can be appreciated between modes, where the
highest performance is achieved by sharing the accelerators.

@@

\section{\uppercase{Discussion}}
\label{sec:discussion}
-Volver a hacer un resumen
-posibles futuras aplicaciones (lab)
-pruebas con otros proveedores o con otras plataformas (azure)

@@

\section{\uppercase{Future work}}
\label{sec:future}
The first task that we should have keep in mind after this study is to upgrade the interconnection network to one more focused on HPC.
So that, porting the setup and the tests to an infrastructure with an Infiniband network would shed light on the viability of this kind of solutions for HPC.

Looking for real situations where the performance is not so important as the flexibility to provide more accelerators. 
Because of that, to take the first steps through how to deploy programming computer labs easily, could be really interesting.

Finally, to bring in more policies to decide the strategy of creating and assigning remote GPUs in the physical device, would be a task to increase the flexibility given by the GPGPU module for Openstack.

>>>>

The other application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, is a classical molecular dynamics simulator that can be applied at the atomic, meso, or continuum scale. 
From the implementation perspective, this multi-process application employs at least one GPU to host its processes, but can benefit from the use of multiple GPUs.
The Subfigure~\ref{subfig:lammps1} shows that running this application using remote GPUs does not offer any advantage in front of original CUDA. 
Furthermore, for the execution on remote GPUs, can be seen a little difference between both networks, the ``High'' network performs worse than ``10 Gb'' network.
Thus, if we compare the results of a LAMMPS execution with a larger problem (see Subfigure~\ref{subfig:lammps2}), although CUDA continues performing better, the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks what means that the transfers are making the interconnection network the bottleneck, and enlarging the problem size
pays off the drawback of a slower network.

@@

\subsection{Experimental Results}
The tests were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1090 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; the cloud platform is deployed by OpenStack; and
the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0.

@@

MCUDA-MEME~\cite{Liu2010} has been the application executed with
different configurations in order to test the set-ups. MCUDA-
MEME is an MPI application which is accelerated by GPUs
Besides, each of its processes must have a GPU to not abort 
So, the number of GPUs will determine the number of processes that we can launch.

The Figure~\ref{fig3} shows and compares the execution time of
the application with different configurations over different setups. 
We have used up to 3 nodes to spread the processes and launched up to 8 processes (only 4 in exclusive mode), one for each remote GPU.
Firstly, we can state that the performance is higher with more than one node, because the traffic network is distributed among the nodes.
Secondly, the lowest execution time is obtained by both modes (exclusive and shared) when running their maximum number of processes with more than 1 node.
It could mean that it is not worthy to continue giving resources to the application to scale, because the performance growth rate is barely increasing.
Although, the time is lower sharing the GPUs the setup cannot take advantage of doubling the devices.

@@

\section{\uppercase{Discussion}}
\label{sec:discussion}
-Volver a hacer un resumen

@@

\section{\uppercase{Future work}}
\label{sec:future}
The first task that we should have keep in mind after this study is to upgrade the interconnection network to one more focused on HPC.
So that, porting the setup and the tests to an infrastructure with an Infiniband network would shed light on the viability of this kind of solutions for HPC.
The same thought, would guide us to try other Cloud vendors which more support for HPC.

Looking for real situations where the performance is not so important as the flexibility to provide more accelerators, 
would drive us to take the first steps through tools for easily deploying programming computer labs with the necessity for GPUs.

Finally, to bring in more strategies to decide where a remote GPUs is created and assigned to a physical device, would be an interesting task to carry out. 
With more scheduling policies the flexibility given by the GPGPU module for Openstack would increase.
